### 2021-05-26 LaTeX-ACM/sections/abstract.tex
edits + resolving merge conflicts

When consumers trade financial products, they typically use well-identified service providers that operate under government regulation. In theory, decentralized platforms like Ethereum can offer trading services `on-chain' without an obvious entry point for regulators. Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons. However this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?

>>>>

When consumers trade financial products, they typically use well-identified service providers that operate under government regulation. In theory, decentralized platforms like Ethereum can offer trading services `on-chain' without an obvious entry point for regulators. Fortunately for regulators, most trading volume in blockchain-based assets is still on centralized service providers for performance reasons. However, this leaves the following research questions we address in this paper: (i) is secure trading (\ie resistant to front-running and price manipulation) even feasible as a fully `on-chain' service on a public blockchain, (ii) what is its performance benchmark, and (iii) what is the performance impact of novel techniques (\eg `roll-ups') in closing the performance gap?
